MCC_Preference_Weak

### 2018-11-28 stats/adults/ex3_comparisons.Rmd
add kids so and pref models

load("mcc_model_comparisons.RData")

@@

likelihood_overview <- bind_rows(
  llh.no.prior.noise,
  llh.rsa.noise,
  llh.prior.noise)

@@

ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)

>>>>

load("mcc_model_comparison.RData")

@@

likelihood_overview <- bind_rows(
  llh.no.prior.noise %>% mutate(Model = "No Prior"),
  llh.rsa.noise %>% mutate(Model = "Pragmatic"),
  llh.prior.noise %>% mutate(Model = "Prior only"))

@@

ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("Log Likelihood per Model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)

### 2018-11-28 stats/adults/mcc_inf2.Rmd
add kids so and pref models

---
title: "MCC Informativeness - moving agent pilots kids"
author: "Manuel Bohn"
date: "7 2 2018"
output: html_document
---

@@

## importing data
d <- novel.data %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
  filter(trial != "7", trial != "8")

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(age,change,trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

@@

p <- d %>%
  filter(trial != "train") %>%
  group_by(change, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .01)+
  geom_pointrange(data = p1, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

---
title: "MCC Informativeness - moving agent"
author: "Manuel Bohn"
date: "7 2 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="inf.2.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

@@

p <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, id) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

### 2018-11-28 stats/adults/mcc_novel.Rmd
add kids so and pref models

---
title: "MCC_Preference"
author: "Manuel Bohn"
date: "26 1 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="pref.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Conditions by agents. Unequal distribution of agents across change leads to seemingly strange patterns for some agents. However, these strange results are always those with very few data points (e.g. Tiger novelty speaker change is only one data point). For those cells with more than five data points, the pattern is very similar to the overall pattern. Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment. This causes the unequal distribution.
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

@@

T-tests against chance for each speaker change conditions
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(change,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

@@

# maximal converging model
lm <- glmer(correct ~ change +
              (1 |id) + (1 |choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

>>>>

---
title: "MCC_Novelty"
author: "Manuel Bohn"
date: "26 1 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="novel.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Conditions by agents. Unequal distribution of agents across change combinations leads to seemingly strange patterns for some agents. However, these strange results are always those with very few data points (e.g. Tiger novelty speaker change is only one data point). For those cells with more than five data points, the pattern is very similar to the overall pattern. Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment. This causes the unequal distribution.
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

@@

T-tests against chance for each change conditions
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(change,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

@@

# maximal converging model
lm <- glmer(correct ~ change +
              (change |id) + (change |choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

### 2018-11-28 stats/adults/mcc_novel.weak.Rmd
add kids so and pref models

---
title: "MCC_Novelty"
author: "Manuel Bohn"
date: "26 1 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="novel.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = change, y = mean, fill = change)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

---
title: "MCC_Novelty_Weak"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="novel.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

### 2018-11-28 stats/adults/mcc_pref.weak3.Rmd
add kids so and pref models

---
title: "MCC_Preference_Weak_Pref/Dispref"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="pref.weak.data5.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

# check if someone needs to be excluded because wrong in training

x <- d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct = mean(correct)) %>%
  filter(correct == 0)

@@

d <- d %>%
  filter(!id %in% x$id)

@@

# Analysis by emotion
```{r plot by emotion}

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,emotion, id) %>%
  summarise(correct = mean(correct))

ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~emotion) +
  labs(x="",y="Proportion Expected Choice")+
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

```{r by emotion}
## model
library(lme4)

data_emo <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))

# maximal converging model
lemo <- glmer(correct ~ change * emotion + (change |id) + (change | choiceAgent), 
              data = data_emo, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lemo)
```

>>>>

---
title: "MCC_Preference_Weak"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

@@

## importing data
d <- read_csv(file="pref.weak.data3.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

# check if someone needs to be excluded because wrong in training
# no one
d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct = mean(correct)) %>%
  filter(correct == 0)

@@

@@
